{{openscpca_module}} Analysis

### 2024-03-21 templates/rmarkdown/notebook-template.Rmd

---
title: "{{module}} Analysis"
author:
  - Your name here
date: "`r Sys.Date()`"
output: html_notebook
---

@@

It is a good idea to start with a brief introduction to the analysis, including the purpose of the analysis, the data used, and the methods applied.
Replace this text with your own introduction, and be sure to update the `title:` and `author:` fields in the YAML header at the top of the document.
Don't forget to rename this files as well!

@@

### Base directories

@@

# The path to this module
module_base <- file.path(repository_base, "analyses", "{{module}}")
```

### Input and output files

@@

# Output files

```

>>>>

---
title: "{{openscpca_module}} Analysis"
author:
  - Your name here
date: "`r Sys.Date()`"
output: html_notebook
---

@@

It is a good idea to start with a brief introduction to the analysis, including the purpose of the analysis, the data used, and the methods applied.
Replace this text with your own introduction, and be sure to update the `title:` and `author:` fields in the YAML header at the top of the document.

Don't forget to rename this file as well!

@@

#### Base directories

@@

# The path to this module
module_base <- file.path(repository_base, "analyses", "{{openscpca_module}}")
```

#### Input and output files

@@

# Output files
```
